My Cool Title

### 2019-05-06 paper.tex
Added conclusion

>>>>

In this work, we present a mobile guidance system that uses an object detector to scan the environment for objects and a POMDP-based controller and audio interface to present the user with guidance instructions. 
We implemented this system into an Android app and tested it with a group of 10 participants to evaluate its effectiveness compared to a baseline, unguided case that only uses the object detector and relies on the human to generate their own search path. 
The key results from these experiment is that the guidance system improved the participants' target-finding performance, reducing the search time and overall camera manipulation effort required.
However, the participants were able to find 8\% more objects on average in the unguided case, but this result was found to be statistically insignificant.

The next steps for the project are to refine and expand the object detector to include objects from other environments.
